---
title: "Diamonds are Forever"
output: html_notebook
---

```{r}
library(ggfortify)
library(mosaic)
library(mosaicData)
library(tidyverse)
library(janitor)
library(GGally)
```
# Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page

```{r}
diamonds <- read_csv("diamonds.csv") %>% clean_names()

head(diamonds)
```


We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r}
alias(lm(carat ~ ., data = diamonds))

?ggpairs
```

```{r}
ggpairs(diamonds, proportions = "auto") # large black unreadable smudge alert
```
```{r}
model1 <- lm(carat ~ x + y + z, data = diamonds)

autoplot(model1)
```


So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}
diamonds_trim <- diamonds %>% 
  select(carat, cut, color, clarity, depth, table, price)

head(diamonds_trim)
```

#We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.
  #Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).
  #Perform further ggplot visualisations of any significant correlations you find.

```{r}
ggpairs(diamonds_trim)
```
```{r}
model2 <- lm(price ~  + carat, data = diamonds_trim)

autoplot(model2)
plotModel(model2)

summary(model2)
```
```{r}
model3 <- lm(price ~ + carat + cut, data = diamonds_trim)

autoplot(model3)
plotModel(model3)

summary(model3)
```

```{r}
model4 <- lm(price ~  + carat + cut + color, data = diamonds_trim)

autoplot(model4)
plotModel(model4)

summary(model4)
```

```{r}
model5 <- lm(price ~  + carat + cut + color, data = diamonds_trim)

autoplot(model5)
plotModel(model5)

summary(model5)
```

```{r}
model6 <- lm(price ~  + carat + cut + color + clarity, data = diamonds_trim)

autoplot(model6)
plotModel(model6)

summary(model6)
```

```{r}
model7 <- lm(price ~  + carat + cut + color + clarity + depth, data = diamonds_trim)

autoplot(model7)
plotModel(model7)

summary(model7)
```

```{r}
model8 <- lm(price ~  + carat + cut + color + clarity + depth + table, data = diamonds_trim)

autoplot(model8)
plotModel(model8)

summary(model8)
```


Shortly we may try a regression fit using one or more of the categorical predictors cut, clarity and color, so let’s investigate these predictors:

Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?

Use the dummy_cols() function in the fastDummies package to generate dummies for these predictors and check the number of dummies in each case.



  
