---
title: "R Notebook"
output: html_notebook
---

#load librarys and read in data, inspect the data
```{r}
library(tsibbledata)
library(tidyverse)
library(dplyr)
library(lubridate)
library(tsibble)
library(slider)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(leaflet)
library(RCurl)
library(jsonlite)

nyc_bikes_df <- nyc_bikes
nyc_bikes_df
```
#add extra columns for day, month, year and trip length
```{r}
nyc_bikes_df <- nyc_bikes_df %>% 
  mutate(
    start_day = yday(start_time),
    start_month = month(start_time),
    start_year = year(start_time),
    trip_length = stop_time - start_time
  )

nyc_bikes_df
```

# mean trip length per day 
```{r}
avg_trip_nyc_bikes <- nyc_bikes_df %>% 
  index_by(start_day) %>% 
  summarise(
    over_day = mean(trip_length)
  )
```

```{r}
avg_trip_nyc_bikes %>% 
ggplot() +
  aes(x = start_day, y = over_day) +
  geom_line()

```

# line graph showing number of customers and subscribers over the span of a year. Note substantially more subscribers than customers. also a large spike in use over the summer time.
```{r}
bike_rentals_over_year<- nyc_bikes %>%
  mutate(time_span = date(start_time), 
         bike_id_new = as.character(bike_id)) %>%
  index_by(time_span) %>%
  group_by(type) %>%
  summarise(count = n())
ggplot(bike_rentals_over_year) + 
  aes(x = time_span, y = count, group = type, color = type) + 
  geom_line()

bike_rentals_over_year
```

# mix of genders hiring over a year, males rent much more often than females
```{r}
gender_bikes <- nyc_bikes %>%
  mutate(time_span = date(start_time), 
         bike_id_new = as.character(bike_id)) %>%
  index_by(time_span) %>%
  group_by(gender) %>%
  summarise(count = n())
ggplot(gender_bikes) + 
  aes(x = time_span, y = count, group = gender, color = gender) + 
  geom_line()

```

# location 
```{r}
nyc_bike_map <- nyc_bikes %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = ~ start_long, 
             lat = ~ start_lat,
             popup = ~ start_station)

nyc_bike_map
```

```{r}
ggplot(nyc_bikes) +
  geom_sf(aes(fill = bike_id)) +
  scale_fill_viridis_c(option = "#56B4E9")
```


