---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
library(janitor)
```


```{r}
cc_tweets <- read_csv("data/code_clan_tweets.csv")

cc_tweets
```

question 1 Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
view(cc_tweets)

head(cc_tweets)
```

```{r}
dim(cc_tweets)
```
```{r}
names(cc_tweets)
```


question 2 Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
cc_tweets %>% 
  filter(is_quote == FALSE) %>% 
  summarise(total = sum(favorite_count))
```

question 3 Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
cc_tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(average_retweet = mean(retweet_count))
```

question 4 Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
cc_tweets %>% 
  mutate(media_type2 = replace_na(media_type, "text")) %>% 
  group_by(media_type2) %>% 
  summarise(fave_total = sum(favorite_count)) %>% 
  arrange(desc(fave_total))
```


question 5 Find the mean number of characters that a CodeClan tweet contains.
```{r}
cc_tweets %>% 
  
```


question 6 The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

question 7 From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.









