---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(modelr)
library(broom)
library(ggfortify)
library(infer)
```
Load the data into a dataframe
```{r}
project<- read_csv("data/project_management.csv")
```
Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()

```

```{r}

```



Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.
```{r}
project %>% 
  summarise(cor_squared = cor(estimated_length, actual_length)^2)
```

# 80% of the data summarise(cor_squared = cor(height, weight)^2)

Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.

```{r}
proj <- lm(formula = estimated_length ~ actual_length, data = project)
```
```{r}
autoplot(proj)
```
Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

```{r}
project <- project %>%
  add_predictions(proj) 

project %>%
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred), col = "red")
```


Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).