---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```
```{r}
msleep <- ggplot2::msleep %>%
  clean_names()

msleep
```
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

H0: udiff_new = 7
Ha: udiff_new ≠ 7

```{r}
msleep %>% 
  ggplot(aes(x = sleep_total)) +
  geom_histogram(col = "white")
```
```{r}
observed_stat <- msleep %>% 
  specify(response = sleep_total) %>% 
  calculate(stat = "mean")

observed_stat
```
```{r}
msleep %>% 
  ggplot(aes(x = sleep_total)) +
  geom_boxplot()
```

```{r}
observed_stat <- msleep %>% 
  summarise(mean_rating = mean(sleep_total))

observed_stat
```

```{r}
null_distribution <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 250000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution
```

```{r}
null_distribution %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_rating,
                direction = "both")
```

```{r}
p_value <- null_distribution %>% 
  get_p_value(obs_stat = observed_stat$mean_rating,
              direction = "both")

p_value
```

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

```{r}
omni<- msleep %>% 
  filter(vore == "omni")

herb <- msleep %>% 
  filter(vore == "herbi")
```

```{r}
omni_herb <- bind_rows(omni, herb)
            
head(omni_herb)
```

```{r}
omni_herb %>% 
  ggplot(aes(x = vore, y = sleep_total)) +
  geom_boxplot()
```

```{r}
null_distribution <- omni_herb %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 20000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_distribution
```

```{r}
observed_stat <- omni_herb %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

observed_stat
```

```{r}
null_distribution %>% 
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "right")
```
```{r}
options(scipen = 999)
p_value <- null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "right")

p_value
```

Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
[Hint - think about creating an is_domesticated variable for the analysis]

```{r}

```


#1.2 Hypothesis testing - interpretation
#1.2.1 Defining the Hypothesis

#For the following three business problems write out H0
#and Ha

#in both mathematical notation and in words. Also state the method you would use to generate the null distribution (bootstrap, permutation or simulation).

# 1 You work for a independent coffee shop. The boss tells you that she thinks that around 40% of people in the town (population 30,000) know of the coffee shop, but you are skeptical of the estimate. You conduct a random survey of 200 people in the town, asking if respondents are aware of your coffee shop. You want to use the sample to test the hypothesis that 40% or more of the town’s population have heard of the coffee shop.

H0: πpop_percent=0.05 40% of the pop have heard of the coffee shop
Ha: πpop_percent≠0,05 40% of the pop have not heard of the coffee shop

i would use bootstrap to develop the null distribution



# 2 You work for a website design company and have performed an A/B test on the position of a banner on a website promoting a particular item.

#A/B testing A method comparing two versions of a web page, email, flyer or other marketing device against each other to determine which version performs better. As it is essentially a controlled experiment, the design should try to ensure that the groups experiencing both versions of the marketing device are equivalent and representative of the population.



#You selected five days at random last month and then randomly selected 200
#of each sampled day’s users into group A and another 200 of that day’s users into group B. Group A continued to be shown the banner at the right hand side of the webpage (its usual position) while group B

#was shown the banner at the top of the page. You monitored each sampled user’s interactions with the website, in particular the ‘click through rate’ (CTR) on the banner, i.e. what proportion of sampled users clicked on the banner. You want to use the sampled data to test the hypothesis that website users overall are more likely to click on the banner if positioned at the top of the page

Ha:top of the page
H0:not at the top of the page

i would use 

# 3 You work as an analyst for a car manufacturing company - they have specific standards they must meet for standards and regulation purposes. You have been asked to check the quality control of the manufacture of a particular car part. You have been given data on a sample of 200 parts produced over the period of a week (the sampled parts were pulled at random from the production line and measured: the factory produced a lot more than 200 parts that week). The specification of the part stipulates a width of 145mm, and the manufacturing process is said to have ‘drifted’ if the mean width of parts differs significantly from 145mm. You want to use the sampled measurements to test whether the process overall has drifted.

Ha: μwidth=145 the width of the part is 145
H0: μwidth≠145 the width of the part if not 145

i would use bootstrap for this since there is multiple measurements of the component to compare 

#For the 3 business problems stated above, imagine we performed you got the following p-values (with the given significance levels) write out your interpretation of the results.

# Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07
we accept the Ha more than 40% of the pop has heard of the coffee shop

# Website company problem. Significance level: 0.01, p-value: 0.006
we reject the Ha users are not more likelly to click on the banner if its at the top of the page
# Manufacturing company problem. Significance level: 0.05, p-value: 0.55
we reject the Ha there is a significant deviation in the part size in the samples