---
title: "R Notebook"
output: html_notebook
---
Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.
```{r}
library(tidyverse)
library(CodeClanData)
```
```{r}
backpack <- CodeClanData::backpack

```
Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(fill = "blue", col = "white") +
  labs(y = "backpacks", x = "weight", bins = 20)
```

Question 3.

Are there differences in backpack weight between sex?
```{r}

ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  geom_bar()
```

Question 4.

What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, y = body_weight) +
  geom_point() +
  labs(x = "backpack weight", y = "body_weight")
```
Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, y = body_weight, colour = sex) +
  geom_point() +
  facet_wrap(~ sex) +
  labs(x = "backpack weight", y = "body weight")
```

Question 6.

What proportion of students report back pain?
```{r}
ggplot(backpack) +
  aes(x = back_problems, fill = back_problems) +
  geom_bar()
```

Question 7.

Is this proportion different between men and women?
```{r}
ggplot(backpack) +
  aes(x = back_problems, fill = back_problems, colour = sex) +
  geom_bar()
```

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

```{r}
ggplot(backpack) +
  aes(backpack_weight, body_weight, sex) +
  geom_line()
```

